---
title: "TidyTuesday Week 52 2020"
author: "Andreas Kitsche"
date: "`r Sys.Date()`"
categories: ["R"]
tags: ["tidytuesday", "R", "python", "rmarkdown"]
bibliography: ["references.bib", "references_auto.bib"]
code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
if (!require("pacman")) install.packages("pacman")
```


```{r packages, include=FALSE}
pacman::p_load(c("reticulate", "bookdown", "knitr", "tidyverse"))
```

```{r bib, include=FALSE}
knitr::write_bib(c("reticulate", "bookdown"), "references_auto.bib")
```


Hey folks,

this is the first of a series of blog post where I want to participate on the [tidytuesday](https://github.com/rfordatascience/tidytuesday/blob/master/README.md) weekly social data project in R. 

> The intent of Tidy Tuesday is to provide a safe and supportive forum for individuals to practice their wrangling and data visualization skills independent of drawing conclusions.

The goal of this series is to help me

* practice data visualization and data wrangling in R (@R-base) using the tidyverse (@tidyverse)
* adopt this skillset to learn Python
* master to publish the applications using [R Markdown](https://bookdown.org/yihui/rmarkdown-cookbook/)

## Results {.tabset .tabset-fade .tabset-pills}

### Tab One

```{r}
head(mtcars)
```

### Tab Two

```{r, fig.dim=c(5, 3)}
par(mar = c(4, 4, .5, .1))
plot(mpg ~ hp, data = mtcars, pch = 19)
```

## {-}

# References